---
title: DATA 606 Data Project Proposal
author: Alexander Niculescu
---


### Libraries
```{r libraries}
library(httr)
library(jsonlite)
library(dplyr)
library(stringr)
library(knitr)
library(readr)
library(ggplot2)

library(reticulate)

```

### Data Preparation
```{bash download-world-cup-of-food-data}
#library(RCurl)
#URL <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/food-world-cup/food-world-cup-data.csv" 
#x = read.csv(file=URL, sep=",", fileEncoding = "UCS-2LE")
mkdir -p ./DATA
curl -s   https://raw.githubusercontent.com/fivethirtyeight/data/master/food-world-cup/food-world-cup-data.csv -o ./DATA/food-world-cup-data.csv
#convert 8859 file to UTF-8
iconv -f ISO-8859-1 -t UTF-8//TRANSLIT ./DATA/food-world-cup-data.csv -o ./DATA/food.csv
```

```{r read-world-cup-of-food-data}
#df <- read.csv("./DATA/food-world-cup-data.csv", header = TRUE, fileEncoding = "UCS-2LE", sep = ",")
#df <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/food-world-cup/food-world-cup-data.csv", header = TRUE)
og <- read.csv("./DATA/food.csv", header = TRUE, sep = ",")
file <- "./DATA/food.csv"
df <- read.csv(file=file, header=TRUE, sep=",")

# parse ratings as integer data type
data <- read_csv(
    file,
    col_types = cols(
        .default = col_integer()
    )
)
data
# select only ratings
df <- data %>% select(-c(2:3, 44:48))

# rename columns as country names
colnames(df) <- str_replace(colnames(df), "^(.+ of )(.+)[:punct:]$", "\\2")
colnames(df)[4] <- "Australia"  # peculiar encoding issue
df_raw <- df
df[is.na(df)] <- 0
df[df != 3]  <- 0

df_raw
```

```{r transform}
#adding keys = RespondId to compare to the og[original gangster] data set later
df$RespondentID <- og$RespondentID

#adding sums vector
df_raw$sum_of_threes <- rowSums( df[2:41] )
df_raw$RespondentID <- og$RespondentID
df_raw$Gender<- og$Gender
df_raw$Age<-og$Age
df_raw$HouseholdIncome<- og$Household.Income
df_raw$Education<- og$Education
df_raw$Location<- og$Location..Census.Region.

df_raw$Gender<- og$Gender


write.csv(df_raw, './DATA/df_raw.csv')
#Turn every 1,2,4,5, N/A into 0's
#matrix <- data.matrix(df)
#matrix
```

You should phrase your research question in a way that matches up with the scope of inference your dataset allows for.**
I want to clean and transform my data first to answer this question: who is most likely to have the blandest taste in America?
A rank of 3 corresponds to bland.  After I've removed all 1's, 2's, 4's, 5's and N/As then I will agreggate 3's accross columns

These are my features:
RespondentID	Generally speaking, how would you rate your level of knowledge of cuisines from different parts of the world?	
How much, if at all, are you interested in cuisines from different parts of the world?
Please rate how much you like the traditional cuisine of [countryName]:
Gender
Age
Household Income	
Education	
Location (Census Region)

### Cases 

**What are the cases, and how many are there?**
Each case represents a contestant at the 2014 food world cup
1374

### Data collection 

**Describe the method of data collection.**
A survey was given at the food world cup, and then I curled it.  
The transformation will be a sum of rank 3 foods.


### Type of study 

**What type of study is this (observational/experiment)?**
This is an observational study


### Data Source 

**If you collected the data, state self-collected. If not, provide a citation/link.**

https://github.com/fivethirtyeight/data/blob/master/food-world-cup/food-world-cup-data.csv


### Dependent Variable

**What is the response variable? Is it quantitative or qualitative?**
Blandness, which is a quantatative intepretation of a food ranking [qualitative.]

### Independent Variable

**You should have two independent variables, one quantitative and one qualitative.**
Education: qualitative
Location: quantatitative
Maybe also add Age, and other demographic features

### Relevant summary statistics 

**Provide summary statistics for each the variables. Also include appropriate visualizations related to your research question (e.g. scatter plot, boxplots, etc). This step requires the use of R, hence a code chunk is provided below. Insert more code chunks as needed.**

After doing the transformation, will have summaries for blandness groupings, which will be filtered by location etc.
Will represent box plots and normal plots interactively using ShinyR and Dplyr

```{r viz-summary}
summary(df_raw$Education)
summary(df_raw$Gender)
summary(df_raw$HouseholdIncome)
summary(df_raw$Location)
summary(df_raw$Age)


#cor(df_raw$sum_of_threes, df_raw$Education)
scatter.smooth(df_raw$sum_of_threes, df_raw$Education)

##Gender
df_raw %>%
  filter(df_raw$sum_of_threes, df_raw$Gender == 'Male') %>%
   summarise(total = n())

df_raw %>%
  filter(df_raw$sum_of_threes, df_raw$Gender == 'Female') %>%
   summarise(total = n())


##Level of Education
df_raw %>%
  filter(df_raw$sum_of_threes, df_raw$Education == 'Some college or Associate degree') %>%
   summarise(total = n())

df_raw %>%
  filter(df_raw$sum_of_threes, df_raw$Education == 'High school degree') %>%
  summarise(total = n())

df_raw %>%
  filter(df_raw$sum_of_threes, df_raw$Education == 'Graduate degree') %>%
   summarise(total = n())

##Household Income
df_raw %>%
  filter(df_raw$sum_of_threes, df_raw$HouseholdIncome == 'Some college or Associate degree') %>%
   summarise(total = n())
```

```{python}
import pandas
import os
myDf = pandas.read_csv("/home/alejandro/Documents/CUNYMS/DATA606/PROJECTS/DATA/df_raw.csv")

```