```{r setup, include=FALSE}
NYTIMES_KEY="b196566ce24f4d3f87fb00daef3bf67f"
```

I googled 'http://www.storybench.org/working-with-the-new-york-times-api-in-r/'
```{r install}
#install.packages("devtools")
#devtools::install_github("mkearney/nytimes")
#install.packages("jsonlite")
```
```{r libraries}
library(jsonlite)
library(dplyr)
```
The usefulness of this API request would be in figuring out the longest running current books on the Best Seller list

As of this submission, HOLY GHOST by John Sandford has been on the best seller list longest.

Of course, I can also do a historical rank for the future.

Lastly, I should probably add a regex to remove or trim off the timestamp from the yyy-mm-dd hh-mm-ss
```{r anotherQuery}
LISTOVERVIEW <- toString(paste("https://api.nytimes.com/svc/books/v3/lists/overview/2018-11-02.json?api-key=", NYTIMES_KEY, sep=""))
y <- fromJSON(LISTOVERVIEW, flatten = TRUE) %>% data.frame()

z <- (y$results.lists.books[1])
names(z) <- c("top_book_list")

cat("Top Books on the Best Seller List, and how many times it has appeared on the list:")
for(i in 1:length(z$top_book_list$author)){
  cat("\n", z$top_book_list$title[i], "by: ", z$top_book_list$author[i], " has been on the best seller list for",            z$top_book_list$weeks_on_list[i], "weeks", "as of", z$top_book_list$created_date[i])
}
```




Sources Cited:
http://www.storybench.org/working-with-the-new-york-times-api-in-r/
https://github.com/NYTimes/public_api_specs/blob/master/books_api/books_api.md
