```{r install, results="hide", include=FALSE}
#install.packages("XML")
#install.packages("pdftools")
```
```{r parser-Libs, results="hide"}
#My collection of useful libraries from the required reading
#library(pdftools)
#library(RCurl)
#library(RHTMLFORMS)
library(XML)
#library(RJSONIO)
library(jsonlite)
#library(rjson)
#library(ROAuth)
#library(SSOAP)
```
Pick three of your favorite books on one of your favorite subjects. At least one of the books should have more than one author. For each book, include the title, authors, and two or three other attributes that you find interesting.

Attributes Chosen: title, author(s), publishing house, length(of book), ISBN-10 Digit

```{r three-books-load}

threeBooksHTML <- "../DATA/books.html"
threeBooksXML  <- "../DATA/books.xml"
threeBooksJSON <- "../DATA/books.json"

HTMLdf <- data.frame(readHTMLTable(threeBooksHTML))
XMLdf  <- xmlToDataFrame(xmlParse(threeBooksXML))
#XML required a shift for the titles to appear
colnames(XMLdf) <- as.character(unlist(XMLdf[1,]))
XMLdf = XMLdf[-1, ]


JSONdf <- data.frame(fromJSON(threeBooksJSON))

HTMLdf; XMLdf; JSONdf

```
```{r test-cases}
(HTMLdf$NULL.Length[2] == XMLdf$Length[2]) && (HTMLdf$NULL.Length[2] == JSONdf$My.Favorite.Books.Length[2])

```

Write R code, using your packages of choice, to load the information from each of the three sources into separate R data frames. Are the three data frames identical?

Yes, the three dataframes are identical(aside from header naming conventions and the character array in the JSON.  However, I can de-nest or flatten the character array if need be!) 