---
title: "HW6"
author: "alexander"
date: "10/31/2018"
output: html_document
---

Chapter 7 - Introduction to Linear Regression
Practice: 7.23, 7.25, 7.29, 7.39
Graded: 7.24, 7.26, 7.30, 7.40

Chapter 8 - Multiple and Logistic Regression
Practice: 8.1, 8.3, 8.7, 8.15, 8.17
Graded: 8.2, 8.4, 8.8, 8.16, 8.18

```{r setup, include=FALSE}

```

7.24 Nutrition at Starbucks, Part I. The scatterplot below shows the relationship between the number of calories and amount of carbohydrates (in grams) Starbucks food menu items con- tain.21 Since Starbucks only lists the number of calories on the display items, we are interested in predicting the amount of carbs a menu item has based on its calorie content.

(a) Describe the relationship between number of calories and amount of carbohydrates (in grams) that Starbucks food menu items contain.
The relationship is a direct poisitive linear correlation
(b) In this scenario, what are the explanatory and response variables?
x(Carbs) is the explanatory, y(Calories) is the response

(c) Why might we want to fit a regression line to these data?
To find whether or not high calorie foods are high in carbs, or to help suggest menu
items for carb sensitive customers.
(d) Do these data meet the conditions required for fitting a least squares line?
Yes, because the residual plot reveals increased frequency at higher calories and tighter bound errors at lower calories.  Least squares should help us fit this accordingly.


7.26 Body measurements, Part III. Exercise 7.15 introduces data on shoulder girth and height of a group of individuals. The mean shoulder girth is 107.20 cm with a standard deviation of 10.37 cm. The mean height is 171.14 cm with a standard deviation of 9.41 cm. The correlation between height and shoulder girth is 0.67.
(a) Write the equation of the regression line for predicting height.
\[
  \hat{height} = beta_0 - beta_1*\hat{shoulder girth}
\]
(b) Interpret the slope and the intercept in this context.
\[
  beta_1 = R * s_y/s_x
\]
```{r 7.26 b}
R <- 0.67
x_mean <- 107.20
y_mean <- 171.14
beta_1 <- 0.67 * (9.41/10.37)
beta_0 <- y_mean - (beta_1*x_mean)
```
(c) Calculate R^2 of the regression line for predicting height from shoulder girth, and interpret it in the context of the application.
```{r 7.26 c}
R_squared <- R * R
```

(d) A randomly selected student from your class has a shoulder girth of 100 cm. Predict the height of this student using the model.
```{r 7.26 d}
x_rand <- 100
y_rand <- beta_0 + beta_1*x_rand
cat("the predicted height of the student is:", y_rand, "cm" )
```
(e) The student from part (d) is 160 cm tall. Calculate the residual, and explain what this residual means.
\[
  e_i = y_i \hat{y}i
\]
```{r 7.26 e}
e_i <- 160 - y_rand
cat("the residual is:", e_i, "cm")
```
A positive residual means that the model underestimates the height.

(f) A one year old has a shoulder girth of 56 cm. Would it be appropriate to use this linear model to predict the height of this child?

 No, this calculation would require extrapolation.
 
 
 7.30 Cats, Part I. The following regression output is for predicting the heart weight (in g) of cats from their body weight (in kg). The coefficients are estimated using a dataset of 144 domestic cats.
 
(a) Write out the linear model.
-0.357 + 4.034 * body_wt
(b) Interpret the intercept.

(c) Interpret the slope.
(d) Interpret R2.
(e) Calculate the correlation coefficient.